Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-24 code/scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
centering tables

To evaluate our progress toward building a cognitive system capable of reasoning about these CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{How well do anchor points capture context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\item{Is the integration of geometric and semantic knowledge necessary?}
\item{Does similarity correlate with performance?}
\end{itemize}

I'm not sure how many of the above questions we want to talk about. The last one is fairly easy and won't take up much space in the paper. The integration of knowledge question is could take some more work as the grouping is determined by semantic type, so in testing just positional knowledge,  I would have to create an alternate set of anchor points.

@@

To determine how non-experts define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for particular region types for each room. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons. The user-provided data provides the ground truth against which we evaluate our transfers.

@@

\begin{equation}
	p=\frac{area(inferred region \cap target region)}{area(inferred region)}
\end{equation}
\begin{equation}
	r=\frac{area(inferred region \cap target region)}{area(target region)}
\end{equation}

As a baseline, we compare the transfer results against our manually encoded CDSRs for the target and a region that represents the entire room. Results on the entire room provide a baseline performance measure. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and a ceiling for the inferred region performance.

\from{Nick}{I'm confused here. Are we comparing the inferred region against our manual region for the target room, or are we comparing our manual region for the target room against the user-provided region for the target room?}

\from{Klenk}{I think that I can do away with all of the stuff about the union from each of the subjects. Especially since we are averaging them all together anyways. We can have a variation in which we control for everything else and vary the user. Perhaps even another table...}

\from{Nick}{Which approach makes the explanation easier, union or averaging? The union makes our target the broadest acceptable region (not the average region though). Averaging shows how well we match an individual's conception of the region on average. Is one of these more relevant to our story than the other?}

\subsection{Results}
\begin{table}
\small
\caption{Performance by Room}
\begin{tabular}{|c|c|c|c|}
\hline
Room & Transfer & Manually Encoded & Entire Room \\
\hline
Classroom-1 & p=nil,r=nil & p=.93,r=.60 & p=.23,r=1 \\
Classroom-2 & p=nil,r=nil & p=.90, r=.69 & p=.19,r=1 \\
Classroom-3 & p=nil,r=nil & p=.94,r=.64 & p=.17,r=1 \\
Classroom-4 & p=nil,r=nil & p=85,r=.89 & p=.19,r=1 \\  %This is 222-Classroom
Classroom-5 & p=nil,r=nil & p=.87,r=.71 & p=.24,r=1 \\ % This is 222-Seminar
Classroom-6 & p=nil,r=nil & p=.76,r=.66 & p=.20,r=.99 \\ % This is UG40
\hline
\end{tabular}
\end{table}

\from{Nick}{Would this be just a single region type or averaging across all applicable ones?}
\from{Klenk}{This is averaging across all applicable ones.}

If we are just going to report means, we should standard deviations as well. %yup!

\begin{table}
\small
\caption{Performance by Region Type}
\begin{tabular}{|c|c|c|c|}
\hline
Region & Transfer & Manually Encoded & Entire Room \\
\hline
Front & p=nil,r=nil & p=.89,r=.79 & p=.23,r=1 \\
Back & p=nil,r=nil & p=.85,r=.82 & p=.13,r=1 \\
Front Rows & p=nil,r=nil & p=.85,r=.48 & p=.22,r=1 \\
Back Rows & p=nil,r=nil & p=.94,r=.40 & p=.7,r=.9 \\
Kitchen & p=nil,r=nil & p=nil,r=nil & p=nil,r=nil \\
Office & p=nil,r=nil & p=nil,r=nil & p=nil,r=nil \\
\hline
\end{tabular}
\end{table}

Or we could report all of the results in a single entry.

\begin{table}
\small
\caption{Performance against Target Region}
\begin{tabular}{|c|c|c|}
\hline
Transfer & Manually Encoded & Entire Room \\
\hline
p=nil,r=nil & p=.88,r=.66 & p=.20,r=.99 \\
\hline
\end{tabular}
\end{table}

% this would be lovely!

Overall the transferred region was significantly better than the entire room (p<Blah), and not statistically different than the manually encoded region (p=Blah). There was a positive correlation (r=Blah) between the structural evaluation score of the analogy and f-measure of the inference.

@@

Our results

>>>>

To evaluate our progress toward building a cognitive system capable of reasoning about CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{Are anchor points able to encode context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\end{itemize}

@@

To determine how people define CDRSs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

@@

\begin{equation}
	p=\frac{area(inferred\ region \cap target\ region)}{area(inferred\ region)}
\end{equation}
\begin{equation}
	r=\frac{area(inferred\ region \cap target\ region)}{area(target\ region)}
\end{equation}

Using this approach we generate results showing the matches between each of the following pairs of regions: the transferred region and the appropriate target region; the manually annotated CDSR in the target and appropriate target region; and the region for the whole room and the target region. 
 Results comparing transferred and target regions measure how well the output of our system matches user expectations. Results comparing the manual annotations to the target regions measure how well the anchor point-based regions we chose match the users' regions (who were not constrained to anchor points). Results comparing whole rooms to target regions provide a baseline performance for comparison.

\subsection{Results}
\begin{table*}
	\center
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.45 $\sigma$=.37, $\bar{r}$=.45 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.29, $\bar{r}$=.66 $\sigma$=.24  & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance}
  \label{tab:overall}

\end{table*}

\from{klenk}{I guess we should rotate the above table. And it has been awhile since I wrote academic, so feel free to cut the boring text below}

Table~\ref{tab:overall} summarizes the results by combining each problem instance and user-defined target region. Both precision and recall for the inferred regions is .45 with a standard deviation of .37 and .38 respectively. When comparing the manually encoded regions against each target instance, we calculate a mean precision of .71 ($\sigma$=.29) and recall of .66 ($\sigma$=.24). The region defined by the room results in a precision of .17 ($\sigma$=.11) and recall of .98 ($\sigma$=.05).

% these are sensible results, nice

\begin{table*}
	\center
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.33 $\sigma$=.34, $\bar{r}$=.52 $\sigma$=.40 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.82 $\sigma$=.19  & $\bar{p}$=.15 $\sigma$=.09, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.45 $\sigma$=.35, $\bar{r}$=.56 $\sigma$=.40 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.62 $\sigma$=.36, $\bar{r}$=.22 $\sigma$=.21 & $\bar{p}$=.82 $\sigma$=.30, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.74 $\sigma$=.28, $\bar{r}$=.43 $\sigma$=.23 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.23 $\sigma$=.03, $\bar{r}$=.09 $\sigma$=.02 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.05 $\sigma$=.01, $\bar{r}$=.06 $\sigma$=.06 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.93 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=0 $\sigma$=0, $\bar{r}$=0 $\sigma$=0 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table*}

Table~\ref{tab:region} separates the results by CDSR type. The mean precision for the transferred regions ranged from .74 for the back rows to 0 for the living room of the studio apartment. Comparing manually encoded against  target regions resulted in a minimum mean precision of .60. This  occurred for the front of the classroom. The whole room precision, which is directly proportionally to the size of the target region, varied from .08 for the office to .35 for the living area.

%(3 :transfer-p (0.5649091160864536d0 . 0.3824746399624735d0)  :transfer-r (0.4264200799557943d0 . 0.34846457388485863d0) :self-p   (0.8290901572528112d0 . 0.19630847005535487d0) :self-r
%  (0.6113880445364026d0 . 0.22432810023132582d0) :room-p
%  (0.20903207305733315d0 . 0.10291204447091876d0) :room-r
%  (0.9960679285191474d0 . 0.011022662977174953d0))
% (2 :transfer-p (0.4496053675639215d0 . 0.36845133415546233d0)
%  :transfer-r (0.4174204919721308d0 . 0.3697742376406773d0) :self-p
%  (0.7556540963495391d0 . 0.2672139547143468d0) :self-r
%  (0.6252647119318083d0 . 0.23778540411202373d0) :room-p
%  (0.17891943994602752d0 . 0.11273973943366206d0) :room-r
%  (0.95742701954372d0 . 0.08432884603590181d0))
% (1 :transfer-p (0.3360804531954755d0 . 0.3364697224078454d0)
%  :transfer-r (0.5074731366878895d0 . 0.4231938085019586d0) :self-p
%  (0.5493333659045643d0 . 0.33190756014975015d0) :self-r
%  (0.7596761147032691d0 . 0.25387231566349d0) :room-p
%  (0.12277614149421091d0 . 0.10953121808467986d0) :room-r
%  (0.9946881982552835d0 . 0.011992196508589958d0))

@@

These results support the hypothesis that anchor points can provide a symbolic representation on top of sensor data for context-dependent spatial regions, and, when combined with qualitative spatial relations, they facilitate learning from a single example through analogical transfer. The relatively high manually encoded precisions and recalls indicate that the defined anchor points are a reasonable starting place for a symbolic representation. The lower scores typically resulted from target regions which were farther away from objects. While the inferred regions did not score as well as the manually encoded regions, they were considerably more precise than the room regions. The only case were transfer was not possible was between the two studio's living room cases. The objects which define the living area in one studio (sofa, TV, and bookshelves) are significantly different than the objects in the other (desk, bed, and sofa), as are the studios in general.
